---
title: "Gender effect in medical study and university positions"
author: "ASHP - EL- FR"
date: "3/30/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,cache=FALSE,verbose=FALSE,message=FALSE,warning=FALSE,include=FALSE,
# base.dir=path <- '~/RT2Lab/gender_effect_faculty/',
autodep = TRUE,
                      cache.path='cache.html')
```

```{r}
library(dplyr)
library(ggplot2)
library(cowplot)
library(stringr)
library(tidyverse)
```


```{r}
library(readxl)
Figures_tables_gender_faculty <- read_excel("~/RT2Lab/databases/core/41_gender_faculty/datas/raw/ecn_2004_2019.xlsx", 
    sheet = "Feuil2")

fig_tab <- Figures_tables_gender_faculty %>% mutate( Suppl_main               = ifelse(Supplemental_or_main == "Supplemental" , "Supp", ""),
		                                          compil_num_fig_table_num = paste0(Suppl_main,Figure_or_Table,nb),
		                                          compil_num_fig_table     = paste0(Suppl_main,Figure_or_Table,nb," : ",pretty_name_title))
```


# ECN Data
Data on ECN ranking were retrieved on the site of the CNG the 30th march 2021, on the following link
https://www.cng.sante.fr/concours-examens/epreuves-classantes-nationales-ecn
Menu "Resultats"

Note that year  2005 (not in the site) and 2008 and 2009 are missing, due to inconvenient formatting.

```{r Preprocessing ECN data}
library(readxl)
library(gtools)
library(lubridate)

ecn <- read_excel("~/RT2Lab/databases/core/41_gender_faculty/datas/raw/ecn_2004_2019.xlsx", 
    col_types = c("numeric", "text", "text", 
        "text", "text", "text", "numeric", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text"))
head(ecn)

# BEWARE, 2 years missing

ecn <- ecn %>% mutate(name = paste(name1,name2,name3,name4,name5,name6) ) %>% 
              filter(!is.na(raw_data))
nrow(ecn) # 95725

ecn$year2 <- as.character(ecn$year)
  
# Preprocess name
ecn$name <- gsub(" NA","",ecn$name)
ecn$name <- gsub(" NA","",ecn$name)
ecn$name <- gsub(" NA","",ecn$name)
ecn$name <- gsub(" NA","",ecn$name)
ecn$name <- gsub(" NA","",ecn$name)
ecn$name <- gsub(" NA","",ecn$name)
ecn$name <- tolower(ecn$name)

duplicated(ecn$name) %>% table()
# FALSE  TRUE 
# 50765 44995 
# Waou! 

# We see that some had several ECN (ex : 2018 - 2019)

# Preprocess first name
ecn$first_name_short   <- str_split_fixed(ecn$first_name, ", ",2)[,1]
ecn$first_name_short2  <- str_split_fixed(ecn$first_name_short, "-",2)[,1]
ecn$first_name_short3  <- tolower(ecn$first_name_short2)
Unaccent <- function(text) {
  text <- gsub("['`^~\"]", " ", text)
  text <- iconv(text, to="ASCII//TRANSLIT//IGNORE")
  text <- gsub("['`^~\"]", "", text)
  return(text)
}

ecn$first_name_short4 <- Unaccent(ecn$first_name_short3)

ecn$name_first_name    <- paste0(ecn$name,"_",ecn$first_name_short4)

## Check 
ecn %>% filter(first_name_short3 == "lauren")
ecn %>% filter(first_name_short3 == "enora")
ecn %>% filter(name == "zaccarini")
ecn %>% filter(name == "hamy") %>% head()
ecn %>% filter(name == "lahousse") %>% head()
ecn %>% filter(name1 == "Colas") %>% head()

# Preprocess gender
ecn$gender <- ifelse(ecn$title == "M.","male","female")
ecn$gender <- factor(ecn$gender, levels = c("female","male"))
ecn %>% group_by(gender) %>% count()
#   gender     n
#   <fct>  <int>
# 1 female 55864
# 2 male   39861

# Preprocess birth date
ecn$new_birth_date <- ifelse(!is.na(ecn$ddn_nom_dusage),ecn$ddn_nom_dusage,ecn$birth_date)
ecn$new_birth_date <- gsub(", ","",ecn$new_birth_date)
ecn$new_birth_date <- gsub("\\.","",ecn$new_birth_date)
ecn$new_birth_date <- gsub(";","",ecn$new_birth_date)
# ecn$new_birth_date <- gsub("é","e",ecn$new_birth_date)
# ecn$new_birth_date <- gsub("û","u",ecn$new_birth_date)

ecn$new_birth_date2 <- dmy(ecn$new_birth_date)
ecn %>% filter(is.na(new_birth_date2)) %>% head() # 129 missing

# Preprocess age at ecn
ecn$date_ecn <- paste0("15-06-",ecn$year2)
ecn$date_ecn <- dmy(ecn$date_ecn)
ecn$age_at_ecn <- round(difftime(ecn$date_ecn,ecn$new_birth_date2)/365,1) %>% as.numeric()

# Ranking
ecn$decile     <- factor(quantcut(ecn$rank_ecn,10), labels= paste0("decile ",c(1:10)))
ecn$quartile   <- factor(quantcut(ecn$rank_ecn,4), labels= paste0("quartile ",c(1:4)))
head(ecn)

ecn <- ecn %>% select(#-raw_data_corrected, 
                      -name_only, -birth_date, - title, -name1, -name2, -name3, -name4, -name5,  -name6,  -nom_dusage,-ddn_nom_dusage,
                      # -first_name_short,
                      -first_name_short2, - first_name_short3,-new_birth_date)
head(ecn)

save(ecn)
```

## Gender repartition and temporal trends

The number of students competing for ecn increased over time.

```{r}
   Dat.label <-  ecn %>% 
      group_by(year2,gender) %>% 
      dplyr::summarise(count=n()) %>%  
      # group_by(tmp) %>% 
      mutate(ypos = cumsum(count) - 0.5*count) %>% 
      mutate(percent_full = count/sum(count)) %>% 
      mutate(percent_format = paste0(round(count/sum(count)*100), '%')) %>% 
      mutate(ypos_percent = cumsum(percent_full) - 0.5*percent_full)  %>%
      mutate(n_and_perc   = paste0("n=", count,", \n (",percent_format,")" ) )   %>%
      ungroup() 

Dat.label$gender2 <- factor(Dat.label$gender, levels= rev(levels(as.factor(Dat.label$gender)) ))

caption_p_nb_students_temporal_trends <- fig_tab[match("p_nb_students_temporal_trends", fig_tab$object_title),"compil_num_fig_table"]
title_p_nb_students_temporal_trends   <- fig_tab[match("p_nb_students_temporal_trends", fig_tab$object_title),"pretty_name_title"]

p_nb_students_temporal_trends <- ggplot(Dat.label, aes(year2, y=count, fill=gender2 )) +
      geom_bar(stat="identity",  width=0.8) +  guides(colour=FALSE)+
      geom_text(data= Dat.label, aes( y = ypos ,label=n_and_perc), size=3.5 ) + 
      # coord_cartesian(ylim = c(0, 110)	) +
      ylab("% cases") + xlab ("") +
      theme(  axis.ticks.x = element_blank() ) + #, legend.position = "none")   + 
      theme_bw()+
      scale_fill_manual(name = "", values =  c("#00BFC4","#F8766D")) +
		labs(title= title_p_nb_students_temporal_trends) 
		     # subtitle="Stromal lymphocytes (%) according to BC subtype",
		     # # caption="Source: mpg",
		     # x="BC subtype",
print(p_nb_students_temporal_trends)

```

0.2% of students passed ECN twice or more.

```{r}
203/95317

ecn %>% group_by(name_first_name, year) %>% count() %>% 
        group_by(n) %>% count()
#       n    nn
#   <int> <int>
# 1     1 95317
# 2     2   201
# 3     3     2


ecn %>% group_by(name_first_name, year,gender) %>% count() %>% 
        group_by(gender,n) %>% count()
#   gender     n    nn
#   <fct>  <int> <int>
# 1 female     1 55637
# 2 female     2   112
# 3 female     3     1
# 4 male       1 39686
# 5 male       2    86
# 6 male       3     1


```



```{r}
ecn %>% group_by(gender) %>%summarise(count=n()) %>%
            		  mutate(percent_format = paste0(round(count/sum(count)*100,1), '%'))
#   gender count percent_format
#   <fct>  <int> <chr>         
# 1 female 55864 58.4%         
# 2 male   39861 41.6%         

   Dat.label <-  ecn %>% 
      group_by(year2,gender) %>% 
      dplyr::summarise(count=n()) %>%  
      # group_by(tmp) %>% 
      mutate(ypos = cumsum(count) - 0.5*count) %>% 
      mutate(percent_full = count/sum(count)) %>% 
      mutate(percent_format = paste0(round(count/sum(count)*100), '%')) %>% 
      mutate(ypos_percent = cumsum(percent_full) - 0.5*percent_full)  %>%
      mutate(n_and_perc   = paste0("n=", count,", \n (",percent_format,")" ) )   %>%
      ungroup() 

   
Dat.label$gender2 <- factor(Dat.label$gender, levels= rev(levels(as.factor(Dat.label$gender)) ))

caption_p_gender_temporal_trends <- fig_tab[match("p_gender_temporal_trends", fig_tab$object_title),"compil_num_fig_table"]
title_p_gender_temporal_trends   <- fig_tab[match("p_gender_temporal_trends", fig_tab$object_title),"pretty_name_title"]

p_gender_temporal_trends <- ggplot(Dat.label, aes(year2, y=percent_full*100, fill=gender2 )) +
      geom_bar(stat="identity",  width=0.8) +  guides(colour=FALSE)+
      geom_text(data= Dat.label, aes( y = ypos_percent*100 ,label=n_and_perc), size=3.5 ) + 
      # coord_cartesian(ylim = c(0, 110)	) +
      ylab("% cases") + xlab ("") +
      theme(  axis.ticks.x = element_blank() ) + #, legend.position = "none")   + 
      theme_bw()+
      scale_fill_manual(name = "", values =  c("#00BFC4","#F8766D")) +
		labs(title= title_p_gender_temporal_trends) 
		     # subtitle="Stromal lymphocytes (%) according to BC subtype",
		     # # caption="Source: mpg",
		     # x="BC subtype",
print(p_gender_temporal_trends)
```

Overall, the gender repartition was predominantly females (n=55864, 58.4%) followed by males (n=39861, 41.6%), and this trend was stable over time.

```{r, include=TRUE, fig.width=12}
p_gender_temporal_trends
```


```{r}
t.test(age_at_ecn  ~ gender, data = ecn)

p_gender_age_ecn <- ggplot(ecn, aes(x=gender, y=age_at_ecn, fill=gender )) +
      geom_boxplot() +
      theme(  axis.ticks.x = element_blank() ) + #, legend.position = "none")   + 
      theme_bw()+
      scale_fill_manual(name = "", values =  c("#00BFC4","#F8766D")) +
  		labs(title= title_p_gender_temporal_trends) 
print(p_gender_age_ecn)

caption_p_histogram_gender_age_ecn <- fig_tab[match("p_histogram_gender_age_ecn", fig_tab$object_title),"compil_num_fig_table"]
title_p_histogram_gender_age_ecn   <- fig_tab[match("p_histogram_gender_age_ecn", fig_tab$object_title),"pretty_name_title"]
  				
p_histogram_gender_age_ecn <- ggplot(ecn, aes(x=age_at_ecn, fill=gender )) +
      geom_histogram(stat="count") +
      theme(  axis.ticks.x = element_blank() ) + #, legend.position = "none")   + 
      theme_bw()+
      scale_fill_manual(name = "", values =  c("#F8766D","#00BFC4")) +
  		labs(title= title_p_histogram_gender_age_ecn,
  		     x = "age") 
print(p_histogram_gender_age_ecn)
```

```{r, include=TRUE, fig.width=12}
p_histogram_gender_age_ecn
```


Median age at ECN was 25.2 y.o. and was significantly different by gender (female : 25.0 y.o versus male : 25.4 y.o, p<0.0001)

```{r}
prenoms_filles <- ecn %>% filter(gender == "female") %>% 
        group_by(first_name_short4) %>% count() %>% arrange(desc(n)) 
top_prenoms_filles <- prenoms_filles[1:20,]

prenoms_garcons <- ecn %>% filter(gender == "male") %>% 
        group_by(first_name_short4) %>% count() %>% arrange(desc(n)) 
top_prenoms_garcons <- prenoms_garcons[1:20,]

```

Top first names showed little diversity (@ASHP to compare to top first names by year)

```{r, include=TRUE}
top_prenoms_filles
top_prenoms_garcons
```

```{r}
p_prenom_filles  <- ggplot(prenoms_filles,aes(x=first_name_short4,y = n))+ geom_bar(  stat="identity") +  theme(  axis.ticks.x = element_blank() ) + #, legend.position = "none")   + 
                    theme_bw()
```

## Ranking at ecn
```{r}
   Dat.label <-  ecn %>% 
      group_by(decile,gender) %>% 
      dplyr::summarise(count=n()) %>%  
      # group_by(tmp) %>% 
      mutate(ypos = cumsum(count) - 0.5*count) %>% 
      mutate(percent_full = count/sum(count)) %>% 
      mutate(percent_format = paste0(round(count/sum(count)*100), '%')) %>% 
      mutate(ypos_percent = cumsum(percent_full) - 0.5*percent_full)  %>%
      mutate(n_and_perc   = paste0("n=", count,", \n (",percent_format,")" ) )   %>%
      ungroup() 

    Dat.label$gender2 <- factor(Dat.label$gender, levels= rev(levels(as.factor(Dat.label$gender)) ))
    
caption_p_gender_deciles <- fig_tab[match("p_gender_deciles", fig_tab$object_title),"compil_num_fig_table"]
title_p_gender_deciles   <- fig_tab[match("p_gender_deciles", fig_tab$object_title),"pretty_name_title"]

    p_gender_deciles <- ggplot(Dat.label, aes(decile, y=percent_full*100, fill=gender2 )) +
      geom_bar(stat="identity",  width=0.8) +  guides(colour=FALSE)+
      geom_text(data= Dat.label, aes( y = ypos_percent*100 ,label=n_and_perc), size=3.5 ) +
      # coord_cartesian(ylim = c(0, 110)	) +
      ylab("% cases") + xlab ("") +
      theme(  axis.ticks.x = element_blank() ) + #, legend.position = "none")   + 
            theme_bw()+
      scale_fill_manual(name = "", values =  c("#00BFC4","#F8766D")) +
  		labs(title= title_p_gender_deciles) 
    print(p_gender_deciles)
```

```{r}
   Dat.label <-  ecn %>% 
      group_by(quartile,gender) %>% 
      dplyr::summarise(count=n()) %>%  
      # group_by(tmp) %>% 
      mutate(ypos = cumsum(count) - 0.5*count) %>% 
      mutate(percent_full = count/sum(count)) %>% 
      mutate(percent_format = paste0(round(count/sum(count)*100), '%')) %>% 
      mutate(ypos_percent = cumsum(percent_full) - 0.5*percent_full)  %>%
      mutate(n_and_perc   = paste0("n=", count,", \n (",percent_format,")" ) )   %>%
      ungroup() 

    Dat.label$gender2 <- factor(Dat.label$gender, levels= rev(levels(as.factor(Dat.label$gender)) ))

caption_p_gender_quartiles <- fig_tab[match("p_gender_quartiles", fig_tab$object_title),"compil_num_fig_table"]
title_p_gender_quartiles   <- fig_tab[match("p_gender_quartiles", fig_tab$object_title),"pretty_name_title"]

    p_gender_quartiles <- ggplot(Dat.label, aes(quartile, y=percent_full*100, fill=gender2 )) +
      geom_bar(stat="identity",  width=0.8) +  guides(colour=FALSE)+
      geom_text(data= Dat.label, aes( y = ypos_percent*100 ,label=n_and_perc), size=3.5 ) +
      # coord_cartesian(ylim = c(0, 110)	) +
      ylab("% cases") + xlab ("") +
      theme(  axis.ticks.x = element_blank() ) + theme_bw()+#, legend.position = "none")   + 
      scale_fill_manual(name = "", values =  c("#00BFC4","#F8766D")) +
  		labs(title= title_p_gender_quartiles) 
    print(p_gender_quartiles)
```

Males were overrepresented in the extremes quantiles when compared with the middle quantiles were females were overrepresented in comparison

```{r, include= TRUE, fig.width=16}
p_gender_quantiles <- plot_grid(p_gender_deciles,p_gender_quartiles, rel_widths = c(10,6))
p_gender_quantiles
```

```{r}
   Dat.label <-  ecn %>% filter(quartile == "quartile 1") %>%
      group_by(year2,gender) %>% 
      dplyr::summarise(count=n()) %>%  
      # group_by(tmp) %>% 
      mutate(ypos = cumsum(count) - 0.5*count) %>% 
      mutate(percent_full = count/sum(count)) %>% 
      mutate(percent_format = paste0(round(count/sum(count)*100), '%')) %>% 
      mutate(ypos_percent = cumsum(percent_full) - 0.5*percent_full)  %>%
      mutate(n_and_perc   = paste0("n=", count,", \n (",percent_format,")" ) )   %>%
      ungroup() 

    Dat.label$gender2 <- factor(Dat.label$gender, levels= rev(levels(as.factor(Dat.label$gender)) ))

caption_p_gender_1stquartiles_by_year <- fig_tab[match("p_gender_1stquartiles_by_year", fig_tab$object_title),"compil_num_fig_table"]
title_p_gender_1stquartiles_by_year   <- fig_tab[match("p_gender_1stquartiles_by_year", fig_tab$object_title),"pretty_name_title"]

    p_gender_1stquartiles_by_year <- ggplot(Dat.label, aes(year2, y=percent_full*100, fill=gender2 )) +
      geom_bar(stat="identity",  width=0.8) +  guides(colour=FALSE)+
      geom_text(data= Dat.label, aes( y = ypos_percent*100 ,label=n_and_perc), size=3.5 ) +
      # coord_cartesian(ylim = c(0, 110)	) +
      ylab("% cases") + xlab ("") +
      theme(  axis.ticks.x = element_blank() ) + theme_bw()+#, legend.position = "none")   + 
      scale_fill_manual(name = "", values =  c("#00BFC4","#F8766D")) +
  		labs(title= title_p_gender_1stquartiles_by_year) 
    print(p_gender_1stquartiles_by_year)
```

Trend analysis showed that the proportion of male in the first quartile increased slightly over time.

```{r, include = TRUE, fig.width=12}
p_gender_1stquartiles_by_year
```

# Hospitalo universitary file
File found of the site of the CNG by Fabien
https://www.cng.sante.fr/sites/default/files/Fichiers/Personnels%20enseignants%20et%20hospitaliers/HU-Liste%20electorale%20au%20%2020%20juin%202019%20final%20publi%C3%A9%20au%2024%20juin%202019.pdf
downloaded the 30 march.
This lists persons voting for the commission statutaire nationale (CSN) at the date of 24 june 2019.

```{r}
library(readxl)
HU_Liste_electorale_au_20_juin_2019_final_publie_au_24_juin_2019 <- read_excel("~/RT2Lab/databases/core/41_gender_faculty/datas/raw/HU-Liste electorale au 20 juin 2019 final publié au 24 juin 2019.xlsx")
head(HU_Liste_electorale_au_20_juin_2019_final_publie_au_24_juin_2019)
hu <- HU_Liste_electorale_au_20_juin_2019_final_publie_au_24_juin_2019 %>% as.data.frame()
head(hu)
nrow(hu) # 6164

hu$name   <- tolower(hu$`Nom de naissance`)
hu$gender <- ifelse(hu$Civilité == "M.","male","female")

# Preprocess first name
hu$first_name   <- tolower(hu$Prénom)
hu$first_name_short2 <- str_split_fixed(hu$first_name, "-",2)[,1]
hu$first_name_short3 <- str_split_fixed(hu$first_name_short2, " ",2)[,1]
hu$first_name_short4 <- Unaccent(hu$first_name_short3)
hu$name_first_name <- paste0(hu$name,"_",hu$first_name_short4)

duplicated(hu$name) %>% table() # 889 duplicated

ecn$name_is_in_hu            <- ifelse(ecn$name %in% hu$name, "yes", "no")
ecn$name_first_name_is_in_hu <- ifelse(ecn$name_first_name %in% hu$name_first_name, "yes", "no")
ecn$admitted_hu              <- ifelse(ecn$name_first_name %in% hu$name_first_name, "HU", "not HU")

```

Overall, 6164 persons were present in the list.

```{r}
hu %>% group_by(gender) %>%summarise(count=n()) %>%
            		  mutate(percent_format = paste0(round(count/sum(count)*100,1), '%'))
#   gender count percent_format
#   <chr>  <int> <chr>         
# 1 female  1844 29.9%         
# 2 male    4320 70.1%     
```

Gender balance favored males in a 70.1/29.9% ratio.

```{r}

   Dat.label <-  hu %>% 
      group_by(gender) %>% 
      dplyr::summarise(count=n()) %>%  
      # group_by(tmp) %>% 
      mutate(ypos = cumsum(count) - 0.5*count) %>% 
      mutate(percent_full = count/sum(count)) %>% 
      mutate(percent_format = paste0(round(count/sum(count)*100), '%')) %>% 
      mutate(ypos_percent = cumsum(percent_full) - 0.5*percent_full)  %>%
      mutate(n_and_perc   = paste0("n=", count,", \n (",percent_format,")" ) )   %>%
      ungroup() 

    Dat.label$gender2 <- factor(Dat.label$gender, levels= rev(levels(as.factor(Dat.label$gender)) ))

    p_gender_hu <- ggplot(Dat.label, aes(gender, y=percent_full*100, fill=gender2 )) +
      geom_bar(stat="identity",  width=0.8) +  guides(colour=FALSE)+
      geom_text(data= Dat.label, aes( y = ypos_percent*100 ,label=n_and_perc), size=3.5 ) +
      # coord_cartesian(ylim = c(0, 110)	) +
      ylab("% cases") + xlab ("") +
      theme(  axis.ticks.x = element_blank() ) + theme_bw()+#, legend.position = "none")   + 
      scale_fill_manual(name = "", values =  c("#00BFC4","#F8766D")) # +
  		# labs(title= title_p_gender_1stquartiles_by_year) 
    print(p_gender_hu)
```


```{r, include = TRUE}
p_gender_hu
```


Out of 6164 persons in the HU list, 533 were found in the ecn list from 2004 to 2019 (representing 7.3% of the total)

```{r}
ecn %>% group_by(name_first_name_is_in_hu) %>% count()
#   name_first_name_is_in_hu     n
#   <chr>                    <int>
# 1 no                       95192
# 2 yes                        533

list_name_first_name_is_in_hu <- ecn %>% filter(name_first_name_is_in_hu == "yes")  %>% select(name_first_name)  %>% as.matrix() %>% as.character()

hu$is_in_ecn_2004_2019 <- ifelse(hu$name_first_name %in% list_name_first_name_is_in_hu, "yes","no" ) 

hu %>% group_by(is_in_ecn_2004_2019) %>%summarise(count=n()) %>%
            		  mutate(percent_format = paste0(round(count/sum(count)*100,1), '%'))
#   is_in_ecn_2004_2019 count percent_format
#   <chr>               <int> <chr>         
# 1 no                   5714 92.7%         
# 2 yes                   450 7.3%          
```


```{r}
   Dat.label <-  ecn %>% 
      group_by(gender,name_first_name_is_in_hu) %>% 
      dplyr::summarise(count=n()) %>%  
      # group_by(tmp) %>% 
      mutate(ypos = cumsum(count) - 0.5*count) %>% 
      mutate(percent_full = count/sum(count)) %>% 
      mutate(percent_format = paste0(round(count/sum(count)*100), '%')) %>% 
      mutate(ypos_percent = cumsum(percent_full) - 0.5*percent_full)  %>%
      mutate(n_and_perc   = paste0("n=", count,", (",percent_format,")" ) )   %>%
      ungroup() 

#   gender name_first_name_is_in_hu count   ypos percent_full percent_format ypos_percent n_and_perc     
#   <fct>  <chr>                    <int>  <dbl>        <dbl> <chr>                 <dbl> <chr>          
# 1 female no                       55705 27852.      0.997   100%                  0.499 n=55705, (100%)
# 2 female yes                        159 55784.      0.00285 0%                    0.999 n=159, (0%)    
# 3 male   no                       39487 19744.      0.991   99%                   0.495 n=39487, (99%) 
# 4 male   yes                        374 39674       0.00938 1%                    0.995 n=374, (1%)  
   
tab <- table(ecn$name_first_name_is_in_hu,ecn$gender, exclude = NULL)   
chisq.test(tab)
   
```

```{r}
ecn %>% filter(name_first_name_is_in_hu == "yes") %>% group_by(gender) %>%summarise(count=n()) %>%
            		  mutate(percent_format = paste0(round(count/sum(count)*100,1), '%'))
#   gender count percent_format
#   <fct>  <int> <chr>         
# 1 female   159 29.8%         
# 2 male     374 70.2%         
```

```{r}
# ICI FAIRE LE PLOT GLOBAL
```



Though women represented 58% of the total of ECN candidates between 2004 and 2019, they represented only 29.8% of those who were admitted to university in this time period.

```{r}
ecn %>% filter(name_first_name_is_in_hu == "yes") %>% group_by(gender) %>%summarise(count=n()) %>%
            		  mutate(percent_format = paste0(round(count/sum(count)*100,1), '%'))
ecn %>% #filter(name_first_name_is_in_hu == "yes") %>%
              group_by(gender) %>%summarise(count=n()) %>%
            		  mutate(percent_format = paste0(round(count/sum(count)*100,1), '%'))

ecn %>% group_by(admitted_hu,gender) %>%summarise(median=median(rank_ecn)) 
wilcox.test(rank_ecn ~ admitted_hu, data = ecn) # 10 -16
wilcox.test(rank_ecn ~ gender, data = ecn) # NS
t.test(rank_ecn ~ gender, data = ecn) # NS
t.test(rank_ecn ~ gender, data = ecn %>% filter(year == "2004")) # very signif
t.test(rank_ecn ~ gender, data = ecn %>% filter(year == "2006")) # very signif
t.test(rank_ecn ~ gender, data = ecn %>% filter(year == "2007")) # very signif
t.test(rank_ecn ~ gender, data = ecn %>% filter(year == "2010")) # no longer signif
t.test(rank_ecn ~ gender, data = ecn %>% filter(year == "2011")) # very signif
t.test(rank_ecn ~ gender, data = ecn %>% filter(year == "2012")) # no signif
t.test(rank_ecn ~ gender, data = ecn %>% filter(year == "2013")) # no signif
t.test(rank_ecn ~ gender, data = ecn %>% filter(year == "2014")) # no signif
t.test(rank_ecn ~ gender, data = ecn %>% filter(year == "2015")) # no signif
t.test(rank_ecn ~ gender, data = ecn %>% filter(year == "2016")) # no signif
t.test(rank_ecn ~ gender, data = ecn %>% filter(year == "2017")) # no signif
t.test(rank_ecn ~ gender, data = ecn %>% filter(year == "2018")) # very signif
t.test(rank_ecn ~ gender, data = ecn %>% filter(year == "2019")) # little signif

wilcox.test(rank_ecn ~ gender, data = ecn %>% filter(year == "2004")) # very signif
wilcox.test(rank_ecn ~ gender, data = ecn %>% filter(year == "2006")) # very signif
wilcox.test(rank_ecn ~ gender, data = ecn %>% filter(year == "2007")) # very signif
wilcox.test(rank_ecn ~ gender, data = ecn %>% filter(year == "2010")) # no longer signif
wilcox.test(rank_ecn ~ gender, data = ecn %>% filter(year == "2011")) # very signif
wilcox.test(rank_ecn ~ gender, data = ecn %>% filter(year == "2012")) # no signif
wilcox.test(rank_ecn ~ gender, data = ecn %>% filter(year == "2013")) # no signif
wilcox.test(rank_ecn ~ gender, data = ecn %>% filter(year == "2014")) # no signif
wilcox.test(rank_ecn ~ gender, data = ecn %>% filter(year == "2015")) # no signif
wilcox.test(rank_ecn ~ gender, data = ecn %>% filter(year == "2016")) # no signif
wilcox.test(rank_ecn ~ gender, data = ecn %>% filter(year == "2017")) # no signif
wilcox.test(rank_ecn ~ gender, data = ecn %>% filter(year == "2018")) # very signif Males better
wilcox.test(rank_ecn ~ gender, data = ecn %>% filter(year == "2019")) # little signif Males better

wilcox.test(rank_ecn ~ gender, data = ecn %>% filter(admitted_hu == "HU")) # NS p = 0.23
wilcox.test(rank_ecn ~ gender, data = ecn %>% filter(admitted_hu == "not HU")) # NS p = 0.60

   Dat.label <-  ecn %>% 
      group_by(admitted_hu,gender) %>% 
      dplyr::summarise(count=n()) %>%  
      # group_by(tmp) %>% 
      mutate(ypos = cumsum(count) - 0.5*count) %>% 
      mutate(percent_full = count/sum(count)) %>% 
      mutate(percent_format = paste0(round(count/sum(count)*100), '%')) %>% 
      mutate(ypos_percent = cumsum(percent_full) - 0.5*percent_full)  %>%
      mutate(n_and_perc   = paste0("n=", count,", \n (",percent_format,")" ) )   %>%
      ungroup() 

    Dat.label$gender2 <- factor(Dat.label$gender, levels= rev(levels(as.factor(Dat.label$gender)) ))

caption_p_gender_hu_or_not <- fig_tab[match("p_gender_hu_or_not", fig_tab$object_title),"compil_num_fig_table"]
title_p_gender_hu_or_not   <- fig_tab[match("p_gender_hu_or_not", fig_tab$object_title),"pretty_name_title"]

    p_gender_hu_or_not <- ggplot(Dat.label, aes(admitted_hu, y=percent_full*100, fill=gender2 )) +
      geom_bar(stat="identity",  width=0.8) +  guides(colour=FALSE)+
      geom_text(data= Dat.label, aes( y = ypos_percent*100 ,label=n_and_perc), size=3.5 ) +
      # coord_cartesian(ylim = c(0, 110)	) +
      # facet_grid(~ admitted_hu) +
      ylab("% cases") + xlab ("") +
      theme(  axis.ticks.x = element_blank() ) + theme_bw()+#, legend.position = "none")   + 
      scale_fill_manual(name = "", values =  c("#00BFC4","#F8766D")) # +
  		labs(title= title_p_gender_hu_or_not) 
    print(p_gender_hu_or_not)
```

```{r, include=TRUE}
p_gender_hu_or_not
```

```{r}
# plot rank ECN among HU
head(ecn)

ecn  %>% filter(name_first_name_is_in_hu == "yes") %>% ggplot(.) +
  geom_boxplot( aes (x = gender ,y = rank_enc, fill = gender)) + 
        facet_grid(~year)

ecn  %>% filter(name_first_name_is_in_hu == "yes") %>% ggplot(aes (x = gender ,y = rank_enc, fill = gender)) +
  geom_boxplot() + 
        facet_grid(~year) +
		  stat_compare_means( # method = "wilcoxon",
		                       label = "p.format", label.x.npc="center")

```




```{r}

   Dat.label <-  ecn %>% filter(name_first_name_is_in_hu == "yes") %>% 
      group_by(year2,gender) %>% 
      dplyr::summarise(count=n()) %>%  
      # group_by(tmp) %>% 
      mutate(ypos = cumsum(count) - 0.5*count) %>% 
      mutate(percent_full = count/sum(count)) %>% 
      mutate(percent_format = paste0(round(count/sum(count)*100), '%')) %>% 
      mutate(ypos_percent = cumsum(percent_full) - 0.5*percent_full)  %>%
      mutate(n_and_perc   = paste0("n=", count,", \n (",percent_format,")" ) )   %>%
      ungroup() 

    Dat.label$gender2 <- factor(Dat.label$gender, levels= rev(levels(as.factor(Dat.label$gender)) ))

caption_p_gender_admitted_HU_by_year <- fig_tab[match("p_gender_admitted_HU_by_year", fig_tab$object_title),"compil_num_fig_table"]
title_p_gender_admitted_HU_by_year   <- fig_tab[match("p_gender_admitted_HU_by_year", fig_tab$object_title),"pretty_name_title"]

    p_gender_admitted_HU_by_year <- ggplot(Dat.label, aes(year2, y=percent_full*100, fill=gender2 )) +
      geom_bar(stat="identity",  width=0.8) +  guides(colour=FALSE)+
      geom_text(data= Dat.label, aes( y = ypos_percent*100 ,label=n_and_perc), size=3.5 ) +
      # coord_cartesian(ylim = c(0, 110)	) +
      ylab("% cases") + xlab ("") +
      theme(  axis.ticks.x = element_blank() ) + theme_bw()+#, legend.position = "none")   + 
      scale_fill_manual(name = "", values =  c("#00BFC4","#F8766D")) +
  		labs(title= title_p_gender_admitted_HU_by_year) 
    print(p_gender_admitted_HU_by_year)

```

Analysis by year did not show a clear trend accross years.

```{r, include=TRUE}
p_gender_admitted_HU_by_year
```

Among those who were admitted in HU position, the quantiles at ECN were represented similarly in males and females, with an overrepresentation of the 3 first deciles admitted in HU positions.

```{r}

   Dat.label1<-  ecn %>% filter(year < 2015,name_first_name_is_in_hu == "yes") %>% 
      group_by(decile) %>% 
      dplyr::summarise(count=n()) %>%  
      # group_by(tmp) %>% 
      mutate(ypos = cumsum(count) - 0.5*count) %>% 
      mutate(percent_full = count/sum(count)) %>% 
      mutate(percent_format = paste0(round(count/sum(count)*100), '%')) %>% 
      mutate(ypos_percent = cumsum(percent_full) - 0.5*percent_full)  %>%
      mutate(n_and_perc   = paste0("n=", count,", \n (",percent_format,")" ) )   %>% mutate(all = "all") %>% 
      ungroup() 
    Dat.label1$decile2 <- factor(Dat.label1$decile, levels= rev(levels(as.factor(Dat.label1$decile)) ))

      Dat.label2 <-  ecn %>% filter(year < 2015,name_first_name_is_in_hu == "yes") %>% 
      group_by(decile, gender) %>% 
      dplyr::summarise(count=n()) %>%  
      group_by(gender) %>% 
      mutate(ypos = cumsum(count) - 0.5*count) %>% 
      mutate(percent_full = count/sum(count)) %>% 
      mutate(percent_format = paste0(round(count/sum(count)*100), '%')) %>% 
      mutate(ypos_percent = cumsum(percent_full) - 0.5*percent_full)  %>%
      mutate(n_and_perc   = paste0("n=", count,", \n (",percent_format,")" ) )   %>%
      ungroup() 
    Dat.label2$decile2 <- factor(Dat.label2$decile, levels= rev(levels(as.factor(Dat.label2$decile)) ))

    p_deciles_ecn_HU_wp <- ggplot(Dat.label1, aes(decile2, y=percent_full*100), fill="lightgrey" ) +
      geom_bar(stat="identity",  width=0.8) +  guides(colour=FALSE)+
      coord_flip(ylim = c(0,40))+
            facet_grid(~all)+
      geom_text(data= Dat.label1, aes( label=n_and_perc),  size=3.5, hjust =  - 0.5 ) +
      # coord_cartesian(ylim = c(0, 110)	) +
      ylab("% cases") + xlab ("") +
      theme(  axis.ticks.x = element_blank() ) + theme_bw()#, legend.position = "none")   + 
  #     scale_fill_manual(name = "", values =  c("#00BFC4","#F8766D")) +
  # 		labs(title= title_p_gender_1stquartiles_by_year) 
    print(p_deciles_ecn_HU_wp)

    p_deciles_ecn_HU_gender <- ggplot(Dat.label2, aes(decile2, y=percent_full*100, fill=gender )) +
      geom_bar(stat="identity",  width=0.8) +  guides(colour=FALSE)+
      coord_flip(ylim = c(0,40))+
      facet_grid(~gender)+
      geom_text(data= Dat.label2, aes( label=n_and_perc),  size=3.5 , hjust =  - 0.5 ) +
      # coord_cartesian(ylim = c(0, 110)	) +
      ylab("% cases") + xlab ("") + theme_bw()+
      theme(  axis.ticks.x = element_blank(), legend.position = "none" ) #)   + 
  #     scale_fill_manual(name = "", values =  c("#00BFC4","#F8766D")) +
  # 		labs(title= title_p_gender_1stquartiles_by_year) 
    print(p_deciles_ecn_HU_gender)
```


```{r}
p_deciles_ecn_HU_wp_and_gender <- plot_grid(p_deciles_ecn_HU_wp,p_deciles_ecn_HU_gender, rel_widths = c(6,12))
p_deciles_ecn_HU_wp_and_gender
```

```{r, include=TRUE}
p_deciles_ecn_HU_wp_and_gender
```


